More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-09-20 2016-Weak-FH-Bisim/WeakBisim.tex
suite...
reunion a l i3s : preuve de decomposition WT -> T

\begin{definition}[pNet composition]
	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$
 can be (partially) filled by providing  a pNets $\pNetQ$ of the
	right sort to fill one of  its holes.	
	Suppose $j_0\in J$:
	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
	%%   K}\myrangle\left[(\pNet'_i)^{i\in L}\right]= \mylangle \pNet_i^{i\in
	%%   I}\left[(\pNet'_i)^{i\in L}\right]\uplus(\pNet'_i)^{i\in J\cap L},S_j^{j\in 
	%%J\setminus L},
	%% \symb{SV}_k^{k\in K}\myrangle
	%% \]
	\[\pNet\left[\pNetQ\right]_{j_0}= \mylangle 
	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNetQ\},\Sort_j^{j\in J\setminus \{j_0\}},
	\overline{\symb{SV}}\myrangle
	\]
\end{definition}

@@

This section defines the semantics of an open \pNet as a translation into an open automaton. 
In this translation, the states of the open automata will be obtained from the states of the \pLTS s at the leaves of the composition. The predicates on the transition will be obtained both from the predicates on the \pLTS s transitions and from the
\TODO{Ce paragraph a eu un probleme, je ne sais pas quand.... Vous avez une vieille version sous la main ?}
This allows us to derive a bismulation theory for open \pNet s. As \pNet s are composition structures, it then makes sense to prove composition lemmas: we prove that the composition of bisimilar pNets are themselves bisimilar.

@@

\paragraph{Variable management.}
The variables in each synchronisation vector are considered local:
for a given pNet expression, we must have fresh local variables for
each occurrence of a vector (= each time we instantiate rule
\TrDeux). Similarly the state variables of each copy of a
given pLTS in the system, must be distinct, and those created for each
application of \TrDeux\ have to be fresh and all distinct. 
This will be implemented within the open-automaton generation algorithm,
e.g. using name generation using a global counter as a suffix.

@@

there exists  open transitions $\symb{OT} \in \mathcal{T}$:

@@

\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \Longleftrightarrow\\  \Bigg( 
 \Big(\alpha = \tau \wedge  \vis{\overline{\beta^2}}=\emptyset \wedge \Pred\,^2 =\symb{True} \wedge \Post^2 =\symb{Id(s)}\Big) \Bigg) \bigvee  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}
where\\
\begin{mathpar} 
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s', \quad
\overline{\gamma}=\biguplus_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^m \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
\end{mathpar}

@@

\begin{proof} ($\Rightarrow$) We proceed by induction on the number of transitions $l$ with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}), in particular we have  $l=n+m+1$.
\begin{itemize}
\item The base case $l=1$, so $n=0$ and $m=0$, then obtain
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule (2) we directly conclude 
 \begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \overline{\beta},\Pred,\Post}
%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.   Induction step is to infer that formula holds for transitions of length $l + 1$. In particular, for $n+1$ or $m+1$, by adding the transition:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
%}
\end{mathpar}

@@

Second by using rule (3) \TODO{To complete}

\end{itemize}
\noindent ($\Leftarrow$) We proceed also  by induction on the number of transitions $l$ with which we  build  a weak transition.

\begin{itemize}
\item Basis: suppose that $\OTWeakarrow {\alpha}$ cannot be subdivided. So for a given weak transition:

\begin{mathpar}
{ \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar}
We have two cases:
\begin{itemize}
\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \symb{True}$ and $\Post=\symb{Id}(s)$. So by rule (2) we have: 
\begin{mathpar}
{ \openrule
         {
           \emptyset,\symb{True},\symb{Id}(s)
				 } {s \OTarrow {\tau} s} \in \mathcal{T}
}
\end{mathpar}
\item Otherwise, by rule (2) we conclude that we have: 
\begin{mathpar}
\openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
\end{mathpar}
where $\overline{\gamma} = \vis{\overline{\beta}}$
\end{itemize}
\item Step: by using rule (3) we can rewrite a weak transition:

@@

\item and 
\begin{mathpar}
\bigg(\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT\bigg)
\Rightarrow
\Bigg(\forall i \in [0\ldots n_2].\openrule
    {
       \overline{\beta'^1_i},\Pred\,'^1_i,\Post'^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge

\openrule
         {
           \overline{\beta'^2},\Pred\,'^2,\Post'^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m_2].\openrule
         {
           \overline{\beta'^3_i},\Pred\,'^3_i,({x^3_k\gets e^3_k})^{k\in K'}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)         
\end{mathpar}
where\\
\begin{mathpar} 
s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2,
\overline{\gamma_2}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta'^1_i}} \dotcup  \vis{\overline{\beta'^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta'^3_i}}
\\
\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\subst{\Post^1_i}

\end{mathpar}
\end{enumerate}

Therefore, we can conclude that:
\begin{mathpar}
\bigg( { \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\bigg)
\!\Rightarrow\!
\Bigg(\!\forall i\! \in\! [0\ldots(n_1\!+\!n_2)].\openrule
    {
       \overline{\beta'^1_i},\Pred\,''^1_i,\Post''^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}}\! \in\!\mathcal{T} \wedge

\openrule
         {
           \overline{\beta'^2},\Pred\,''^2,\Post''^2 }
         {s^2 \OTarrow {\alpha} s'^2}\! \in\! \mathcal{T}
\!\wedge
\forall i\! \in\! [0\ldots(m_1\!+\!m_2)].\openrule
         {\overline{\beta'^3_i},\Pred\,''^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i\OTarrow {\tau} s^3_{i+1}}\!\in\!\mathcal{T}\!\Bigg)  
\end{mathpar}

where\\
\begin{mathpar} 
s_1=s^1_0 \wedge s^1_{n_1+n_2}=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}=s'\\
\overline{\gamma}=\biguplus_{i=0}^{n_1+n_2} \vis{\overline{\beta'^1_i}} 
\dotcup  \vis{\overline{\beta'^2}} \dotcup \biguplus_{i=0}^{m_1+m_2} \vis{\overline{\beta'^3_i}}
\\
\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\subst{\Post^1_i}
\end{mathpar}

\begin{mathpar}
\forall i \in [0\ldots m_1].\openrule
    {
       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         
\end{mathpar}

such that\\
\begin{mathpar} 
s_2=s^3_0 \wedge s^1_{m_1}=s' \quad
\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}} 
\quad
\Pred_3=\bigwedge_{i=0}^{m_1}\Pred^3_i\quad \Post_3= \biguplus_{i=0}^{m_1} \Post_i^3
\end{mathpar}

\end{itemize}
\end{proof}

------------------------------------------------------

>>>>

\begin{definition}[pNet composition]
	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$
 can be (partially) filled by providing  a pNet $\pNetQ$ of the
	right sort to fill one of  its holes.	
	Suppose $j_0\in J$:
	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
	%%   K}\myrangle\left[(\pNet'_i)^{i\in L}\right]= \mylangle \pNet_i^{i\in
	%%   I}\left[(\pNet'_i)^{i\in L}\right]\uplus(\pNet'_i)^{i\in J\cap L},S_j^{j\in 
	%%J\setminus L},
	%% \symb{SV}_k^{k\in K}\myrangle
	%% \]
	\[\pNet\left[\pNetQ\right]_{j_0}= \mylangle 
	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNetQ\},\Sort_j^{j\in J\setminus \{j_0\}},
	\overline{\symb{SV}}\myrangle
	\]
\end{definition}

@@

This section defines the semantics of an open pNet as a translation into an open automaton. 
In this translation, the states of the open automata will be obtained from the states of the \pLTS s at the leaves of the composition. The predicates on the transition will be obtained both from the predicates on the \pLTS s transitions and from the
\TODO{Ce paragraph a eu un probleme, je ne sais pas quand.... Vous avez une vieille version sous la main ?}
This allows us to derive a bismulation theory for open pNets. As pNets are composition structures, it then makes sense to prove composition lemmas: we prove that the composition of bisimilar pNets are themselves bisimilar.

@@

\paragraph{Variable management.}
The variables in each synchronisation vector are considered local:
for a given pNet expression, we must have fresh local variables for
each occurrence of a vector (i.e. each time we instantiate rule
\TrDeux). Similarly the state variables of each copy of a
given pLTS in the system, must be distinct, and those created for each
application of \TrDeux\ have to be fresh and all distinct. 
This will be implemented within the open-automaton generation algorithm,
e.g. using name generation using a global counter as a suffix.

@@

\end{mathpar}  
\TODO{!!! FAUX -- to REMOVE}
there exists  open transitions $\symb{OT} \in \mathcal{T}$:

@@

-\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)  \Longleftrightarrow  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}
where\\
\begin{mathpar} 
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s', \quad
\overline{\gamma}=\biguplus_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^m \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
\end{mathpar}

@@

\begin{proof} ($\Rightarrow$) We proceed by induction on  $l=n+m+1$, which is in fact
the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
\begin{itemize}
\item The base case $l=1$, so $n=0$ and $m=0$, then obtain
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule (2) we directly conclude 
 \begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \overline{\beta},\Pred,\Post}
%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.   Induction step is to infer that formula holds for transitions of length $l + 1$. As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively).
We consider the case $n'=n+1$, $m'=m+1$ is similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction
Suppose
$
\Bigg(\forall i \in [0\ldots n+1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg) $

By recurrence hypothesis the theorem is true for any set of transitions of length $l$. In particular, we have

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)  \implies  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}

We need to prove the same implication with

 by adding the transition:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
%}
\end{mathpar}

@@

By rule (1) we have
${ \openrule
         {
          \emptyset,True,Id(s')
				 } {s' \OTWeakarrow {\tau} s'} \in \WT
}$
Finally by using rule (3) we compose the three rules:

\TODO{todo}

The right part of the disjunction, i.e.
\begin{mathpar}
\Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)
\end{mathpar}
is handled trivially by rule (WT1)

\end{itemize}
\TODO{add rule numbers WT1 WT2 WT3, and refer to them}

\noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition.

\begin{itemize}
\item case rule (WT1):
\begin{mathpar}
{ \openrule
         {
           \emptyset,\symb{True},\symb{Id}(s)
				 } {s \OTarrow {\tau} s} \in \mathcal{T}
}
\end{mathpar}
In this case we can directly conclude by the right part of the disjunction.

\item case rule (WT2). \TODO{write inference}
\begin{mathpar}
\openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
\end{mathpar}

This proves the implication with $n=0$ and $m=0$.

\item case rule (WT3).
\TODO{put WT3 here}

%
%
%Basis: suppose that $\OTWeakarrow {\alpha}$ cannot be subdivided. So for a given weak transition:
%
%\begin{mathpar}
%{ \openrule
%         {
%           \overline{\gamma}\!,\Pred,\Post
%				 } {s \OTWeakarrow {\alpha} s'} \in \WT
%}
%\end{mathpar}
%We have two cases:
%\begin{itemize}
\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \symb{True}$ and $\Post=\symb{Id}(s)$. So by rule (2) we have:

\item Otherwise, by rule (2) we conclude that we have:

where $\overline{\gamma} = \vis{\overline{\beta}}$
\end{itemize}
\item Step: by using rule (3) we can rewrite a weak transition:

@@

\item and 
\begin{mathpar}
\bigg(\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT\bigg)
\Rightarrow
\Bigg(\forall i \in [0\ldots n_2].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge

\openrule
         {
           \overline{\beta^2},\Pred^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m_2].\openrule
         {
           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)         
\end{mathpar}
where\\
\begin{mathpar} 
s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2,
\overline{\gamma_2}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta^3_i}}
\\
\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
\\
\Post_2= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
\end{mathpar}
\end{enumerate}

Therefore, we can conclude that:
\begin{mathpar}
\bigg( { \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\bigg)
 \Rightarrow
\Bigg(\forall i\in [0\ldots(n_1\!+\!n_2)].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in\mathcal{T} \wedge

\openrule
         {
           \overline{\beta^2},\Pred^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\wedge
\forall i \in [0\ldots(m_1\!+\!m_2)].\openrule
         {\overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i\OTarrow {\tau} s^3_{i+1}}\in\mathcal{T}\Bigg)  
\end{mathpar}

where\\
\begin{mathpar} 
s_1=s^1_0 \wedge s^1_{n_1+n_2}=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}=s'\\
\overline{\gamma}=\biguplus_{i=0}^{n_1+n_2} \vis{\overline{\beta^1_i}} 
\dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_1+m_2} \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
\\
\Post= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
\end{mathpar}

\end{proof}
-----------------------------------------------------
